---
title: "SGN biophysical properties are associated with its hair cell contact position"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load and format data

Biocytin-labelled SGN were recorded via patch-clamp electrophysical procedures to associate whole-cell biophysical properties of individual SGN with its afferent projection contact position onto inner and outer hair cells.

The following is a data spreadsheet with specimen annotations, morphological, current- and voltage- clamp measurements:

```{r sgn_spreadsheet, echo=TRUE}
### LOAD DATA #################################################################
sgn_data <- read.delim(
    "Derived/2022-03-21_SGN_ephys_morphology_spreadsheet.txt"
    );
### FORMAT DATA ###############################################################
sgn_cc_features <- c("Graded.Index", "Current.Threshold",
                          "Voltage.Threshold", "Vm", "AP.Height",
                          "AP.Latency.threshold");
sgn_vc_features <- c("Peak.Current", "SS.Current", "ss.30", "ss.max", "g.30",
                     "gmax", "Vmid", "g30.gmax", "Outward.inactivation.tau");
sgn_animal_info <- c("Age", "MP.Classification", "CDR", "Branch.Number");

cat("Current clamp features:")
str(sgn_cc_features)
cat("Voltage clamp features:")
str(sgn_vc_features)
```
```{r, echo=FALSE}
### FORMAT DATA GROUPS #########################################################
sgn_data$SGN.Type[sgn_data$SGN.Type == ""]     <- NA;
sgn_data$Spike.Type[sgn_data$Spike.Type == ""] <- NA;

sgn_data$SGN.Type   <- factor(sgn_data$SGN.Type);
sgn_data$Spike.Type <- factor(sgn_data$Spike.Type);
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
